Results

### 2025-04-24 notebooks/00_index.qmd
update

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
using GLMakie
using Statistics
# using CairoMakie
using Dates
using PartialFunctions
using Unitful
using Beforerr: _theme_legend
using SPEDAS.SpaceDataModel: set, extend, @set
using PSPAnisotropy
include("../src/psp_temp.jl")
include("../src/calc.jl")
using PSPAnisotropy: Wind, PSP, THEMIS

@@

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-21")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")
_tmax_wind = DateTime("2021-01-15T02")

tmin_psp = DateTime("2021-01-16")
tmax_psp = DateTime("2021-01-19")
# tmin_wind = DateTime("2021-01-17")
# tmax_wind = DateTime("2021-01-18")

B_ylabel = "B (nT)"
B_labels = ["Bx", "By", "Bz", "Magnitude"]
n_ylabel = ulabel("Density", "cm^-3")
V_ylabel = "V (km/s)"
ΔV_ylabel = "ΔV (km/s)"
V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
Temp_ylabel = "Temperature (eV)"

V_mva_labels = ["V_L", "V_M", "V_N"]
B_mva_labels = ["B_L", "B_M", "B_N"]
```

```{julia}
tvars_psp = [
    tnorm_combine ∘ PSP.B,
    PSP.n,
    PSP.V,
    PSP.T
]
```

```{julia}
tvars_wind = [
    tnorm_combine ∘ Wind.B,
    Wind.n,
    # tsubtract ∘ SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
    tsubtract ∘ Wind.V,
    Wind.temp
]
```

```{julia}
tvars_themis = [
    tnorm_combine ∘ THEMIS.B_GSE,
    THEMIS.n,
    THEMIS.V_GSE,
    THEMIS.T,
]
```

```{julia}
f = Figure(; size=(1200, 800))
add_title = false
legend = (; position=Top())
# plot = (; resample=(; n=Inf))
labels = '1':'9'
tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title, legend)
add_labels!(f[1, 1]; labels, open="(a.")

# tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title, legend)
# add_labels!(f[1, 2]; labels, open="(b.")

# tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; add_title, legend)
# add_labels!(f[1, 3]; labels, open="(c.")
f
```

>>>>

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
# using CairoMakie
using GLMakie
using Statistics
using Dates
using PartialFunctions
using Unitful
using Beforerr: _theme_legend, easy_save
using SPEDAS.SpaceDataModel: set, extend, @set
using PSPAnisotropy
include("../src/psp_temp.jl")
include("../src/calc.jl")
include("../src/meta.jl")
using PSPAnisotropy: Wind, PSP, THEMIS

@@

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-20")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")
_tmax_wind = DateTime("2021-01-15T02")

tmin_psp = DateTime("2021-01-16")
tmax_psp = DateTime("2021-01-19")
# tmin_wind = DateTime("2021-01-17")
# tmax_wind = DateTime("2021-01-18")
```

```{julia}
tvars_psp = [
    set(tnorm_combine ∘ PSP.B_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
    set(PSP.n; ylabel=n_ylabel),
    set(tnorm_combine ∘ PSP.V; ylabel=V_ylabel, labels=V_RTN_labels),
    set(PSP.T; ylabel=T_ylabel)
]
```

```{julia}
tvars_wind = [
    set(tnorm_combine ∘ Wind.B_RTN_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
    set(Wind.n; ylabel=n_ylabel),
    set(Wind.V_RTN; ylabel=V_ylabel, labels=V_RTN_labels),
    set(Wind.T; ylabel=T_ylabel)
]
```

```{julia}
using Intervals: Interval
data = THEMIS.V_GSE(tmin_wind, tmax_wind)
_times = @views SPEDAS.times(data)[(data[:, 1].>-200u"km/s").|(data[:, 2].<-50u"km/s")]
dt = Minute(10)
its = union([Interval(t - dt, t + dt) for t in _times])
_tmask! = tmask!(its)
```

```{julia}
tvars_themis = [
    set(_tmask! ∘ tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
    THEMIS.n,
    _tmask! ∘ THEMIS.V_GSE,
    set(THEMIS.T; ylabel=T_ylabel)
]

```

```{julia}
tmin_psp = "2021-01-14"
tmax_psp = "2021-01-20"

f = Figure(; size=(900, 600))
legend = (; position=Top())
labels = '1':'9'
# plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
# add_labels!(f[1, 1]; labels, open="(a.")

# tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
# add_labels!(f[1, 2]; labels, open="(b.")

tplot(f[1, 1], tvars_themis, tmin_wind, tmax_wind; legend)
add_labels!(f[1, 1]; labels, open="(c.")
f
# easy_save("overview")
```
